---
title: "Reproducible documents"
author: "Aino R. Peltonen"
format: html
---
- Aino R. Peltonen, MSc.
- PhD Fellow, Anne Loft's groups, FGM, BMB, SDU
- Affiliation NNFC at Broad Institute

# Intro
In this thesis **we** will study *how* adipose tissue and liver communicate in obesity.

# Methods and Results
There's something light about *wet lab* but the main emphasis will be in **computational tools**.

## Analysis
We analyzed **so** much.

# Discussion
And then we have some *deep* remarks of biology and how our findings take science **forward**.

```{r setup}
#| message: false
#| warning: false
#| echo: false
library(tidyverse)
library(NHANES)
nhanes_small <- read_csv(here::here("data/NHANES_small.csv"))
```

```{r}
nhanes_small <- select(nhanes_small, age, sex, bmi, diabetes, phys_active, bp_sys_ave, bp_dia_ave, education)
nhanes_small
```


```{r}
2 + 2
```
# Table of results
```{r}
nhanes_small %>%
  filter(!is.na(diabetes)) %>%
  group_by(diabetes, education) %>%
  summarise(
    mean_age = round(mean(age, na.rm = TRUE), 2),
    mean_bmi = mean(bmi, na.rm = TRUE) %>%
      round(3)
  ) %>%
  ungroup() %>%
  knitr::kable(caption = "Mean values of age and BMI for education and diabetes status")
```

## Prettier table
```{r}
#| echo: false
#| warning: false
nhanes_small %>%
  filter(!is.na(diabetes), !is.na(education)) %>%
  group_by(diabetes, education) %>%
  summarise(
    mean_age = mean(age, na.rm = TRUE),
    mean_bmi = mean(bmi, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(
    # Task 2a.
    mean_age = round(mean_age, 1),
    mean_bmi = round(mean_bmi, 1),
    # Task 2b.
    education = str_to_sentence(education)
  ) %>%
  rename(
    # Task 3.
    "Diabetes status" = diabetes,
    "Education" = education,
    "Mean Age" = mean_age,
    "Mean BMI" = mean_bmi
  ) %>%
  knitr::kable(caption = "Mean values of Age and BMI for each education and diabetes status.")
```
